Journey: A Study of Scalabilty of Memory Management in Linux

### 2017-05-05 paper.tex
Fix some part of 4.1.2

\begin{figure}[t]
    \includegraphics[width=\columnwidth]{figures/mmap_mem_usage}
    \caption{$\Delta_i$ adjusted with \texttt{control} for benchmarks. Note that
    graphs of \texttt{frag} and \texttt{stride} overlap. Also, \texttt{cont} and
    \texttt{control} overlap.}
    \label{fig:mmap_mem_usage}
\end{figure}

\begin{figure}[t]
    \includegraphics[width=\columnwidth]{figures/vm_area_struct_count}
    \caption{Number of \texttt{vm\_area\_struct}s for benchmarks.}
    \label{fig:vm_area_struct_count}
\end{figure}

@@

It can be seen that for continuous \texttt{mmap}s the time is not only the
lowest but is also invariant with the total number of \texttt{mmap}s done so
far. There are two reasons for this.

@@

For the other workloads, a search through the red-black tree is often needed on
most accesses. This operation takes $O(log n)$ time, where $n$ is the number of
virtual memory areas. The logarithmic behavior is visible in the plots for the
benchmarks in Figure \ref{fig:mmap_latency}.

>>>>

\begin{figure}[t]
    \includegraphics[width=\columnwidth]{figures/mmap_mem_usage}
    \caption{$\Delta_i$ as discussed in section \ref{ss_vm_area_struct}. Note that
    graphs of \texttt{frag} and \texttt{stride} overlap. Also, \texttt{cont} and
    \texttt{control} overlap.}
    \label{fig:mmap_mem_usage}
\end{figure}

\begin{figure}[t]
    \includegraphics[width=\columnwidth]{figures/vm_area_struct_count}
    \caption{Number of \texttt{vm\_area\_struct}s. The graphs of
    \texttt{control} and \texttt{cont} workloads are almost coincident with the
    x-axis.}
    \label{fig:vm_area_struct_count}
\end{figure}

@@

For continuous \texttt{mmap}s the time is not only the lowest of any benchmark
but is also invariant with the total number of \texttt{mmap}s done so far.
There are two reasons for this.

@@

For the other workloads, a search through the red-black tree is often needed on
most accesses. This operation takes $O(\log n)$ time, where $n$ is the number of
virtual memory areas. The logarithmic behavior is visible in the plots for the
benchmarks in Figure \ref{fig:mmap_latency}.
